Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-06 paper/paper-nature_format.qmd
Update MPs

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where the Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Finally, we discuss the script we developed to fill in remaining missing details on the member of parliament speaking, which each file in our database was passed to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the member of parliament whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the member of parliament who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

@@

While the modifications needed to develop the second script were straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the person who made each statement, such as their party and electorate.

@@

A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period of each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the member continued their speech. Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

@@

Having these lists enabled us to extract the names of members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns. We then used these extracted names to split all the speeches, using regular expressions with lookarounds. A lookaround can be added to a regular expression pattern to enhance the specificity of matches. These were used to ensure that the text was not being split in the wrong places, such as places where members were being named in the statement of another member.

@@

Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender, and unique ID information. Finally, we were able to add a flag for interjections. Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not the Speaker, the Deputy Speaker, or the member whose turn it was to speak. @fig-interject provides an example of a Federation Chamber proceeding with interjections. Statements made by the member whose turn it was to speak, or by the Deputy Speaker Maria Vamvakinou, are not flagged as interjections.

@@

We then proceeded to clean up speeches and fill in correct details on the member of parliament speaking. While we used the same lookup table approach as before, we did so in combination with another means of filling in these details. The patterns parsed from `<talk.start>` nodes contain important data on the member of parliament making each statement. As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `"talk.start/talker"`. We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement. @fig-patterns provides an example of that lookup table. This approach enabled us to fill in missing data on each member of parliament speaking using data extracted directly from the XML. Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by members. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected 129 dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one member repeating the words of another member would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.

When a member runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word. As a means of checking that we have separated speeches out correctly, our third test checks that when the phrase "(Time expired)" exists in a body of text, it exists at the very end. When this is not the case, we know that we have missed the separation of the next statement onto its own row, and could fix this accordingly.

The remaining tests focus on the members present on each sitting day. Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day. As we parsed Hansard further back in time, we found a number of cases where an individual was associated with the wrong electorate or party due to transcription errors. When we found these data errors we corrected them based on the official release. This test provides us with an automated way to catch these errors and correct them at scale.

@@

Our sixth test checks that on any given sitting day, the individuals identified are alive. To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician. This test confirmed that all members who are detected to speak on each sitting day are not deceased.

Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day. We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament. Using these dates, we check that each person speaking on each sitting day is in fact a member of parliament on that day.

@@

Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament. For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings. In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01. Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`. Importantly, in our work we focus primarily on parsing spoken speech content (i.e. what is nested within `<speech>` nodes), such as what is stated by the Speaker in @fig-content_ex. For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database. In future work, capturing this unspoken content in our database would be a priority.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each CSV file. This serves as a unique identifier for each speaking Member, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages.

Further, the `name.id` variable found in each CSV is another unique identifier for each member of parliament. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each member of parliament in a tidy, ready to analyze format.

@@

The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj. All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in member details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

>>>>

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

The Australian House of Representatives 'the House' performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. Politicians in the House are referred to as Members of Parliament (MPs). The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all MPs from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where is the Speaker tells that MP to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Finally, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

@@

While the modifications needed to develop the second script were straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by an MP, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the MP who made each statement, such as their party and electorate.

@@

A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period of each sitting day in the Chamber where MPs can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all MPs in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When an MP interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

@@

Having these lists enabled us to extract the names of MPs and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns. We then used these extracted names to split all the speeches, using regular expressions with lookarounds. A lookaround can be added to a regular expression pattern to enhance the specificity of matches. These were used to ensure that the text was not being split in the wrong places, such as places where MPs were being named in the statement of another MP.

@@

Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender, and unique ID information. Finally, we were able to add a flag for interjections. Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not the Speaker, the Deputy Speaker, or the MP whose turn it was to speak. @fig-interject provides an example of a Federation Chamber proceeding with interjections. Statements made by the MP whose turn it was to speak, or by the Deputy Speaker Maria Vamvakinou, are not flagged as interjections.

@@

We then proceeded to clean up speeches and fill in correct details on the MP speaking. While we used the same lookup table approach as before, we did so in combination with another means of filling in these details. The patterns parsed from `<talk.start>` nodes contain important data on the MP making each statement. As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `"talk.start/talker"`. We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement. @fig-patterns provides an example of that lookup table. This approach enabled us to fill in missing data on each MP speaking using data extracted directly from the XML. Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where an MP spoke whose surname was shared by any other past or present MP, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected 129 dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.

When an MP runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word. As a means of checking that we have separated speeches out correctly, our third test checks that when the phrase "(Time expired)" exists in a body of text, it exists at the very end. When this is not the case, we know that we have missed the separation of the next statement onto its own row, and could fix this accordingly.

The remaining tests focus on the MPs present on each sitting day. Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day. As we parsed Hansard further back in time, we found a number of cases where an individual was associated with the wrong electorate or party due to transcription errors. When we found these data errors we corrected them based on the official release. This test provides us with an automated way to catch these errors and correct them at scale.

@@

Our sixth test checks that on any given sitting day, the individuals identified are alive. To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician. This test confirmed that all MPs who are detected to speak on each sitting day are not deceased.

Finally, our seventh test validates that all individuals speaking are MPs on that particular day. We use the `mps` dataset from the `AustralianPoliticians` package which has the dates when each MP was in parliament. Using these dates, we check that each person speaking on each sitting day is in fact an MP on that day.

@@

Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament. For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular MP and was not spoken aloud during the parliamentary proceedings. In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01. Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`. Importantly, in our work we focus primarily on parsing spoken speech content (i.e. what is nested within `<speech>` nodes), such as what is stated by the Speaker in @fig-content_ex. For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database. In future work, capturing this unspoken content in our database would be a priority.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each CSV file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages.

Further, the `name.id` variable found in each CSV is another unique identifier for each MP. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.

@@

The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj. All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
